\documentclass{article}
\usepackage[letterpaper,margin=1in,top=0.5in]{geometry}

\title{Proposal: Small-World Behavior in Time-Varying Interaction Networks of
  Mobile Agents}
\author{Will Vining}

\begin{document}
\maketitle

\section{Introduction}
This paper will investigate the emergence of small-world behavior in
time-varying graphs that represent the interactions between mobile
agents. This builds on the work of Tang et al~\cite{Tang2010} who
modeled time-varying interaction networks for agents moving in a
finite space and periodically making large jumps to a distant
location. I intend to model a more physically plausible scenario where
agents cannot be ``teleported'' in this way. I will investigate
whether small-world behavior emerges without ``teleportation,'' and if
so how many agents are required for the interaction network to exhibit
this behavior. I will also investigate whether the properties of the
interaction network change if agents employ different motion
rules. Finally, I will examine communicability over these time-varying
graphs using the method presented by Casteigts et
al.~\cite{Grindrod2011}.

\section{Computational Methods}
\label{sec:comp-methods}
A model of agents moving in a finite space will be used to generate
time-varying interaction networks. Agent movement will be continuous,
and agent positions will be sampled a total of $T$ times at a fixed
rate to determine the interaction network at each time-step. As
in~\cite{Tang2010} an edge will be added between agents at time $t$ if
they are within some fixed distance $d$ of each-other. For ease and
simplicity agents will be modeled as particles and collisions will not
be considered.  I will implement the ``teleportation'' movement
described in~\cite{Tang2010} as well as Brownian motion, a L{\'e}vy
flight, and a correlated random walk.

%% Talk to Melanie about whether this is a good null model

\section{Experimental Methods}
I will use the agent-based model described in
section~\ref{sec:comp-methods} to generate 10 interaction networks for
10, 100, 1000, and 10000 agents and each type of motion
(Teleportation, Brownian motion, L{\'e}vy flight, and Correlated
Random Walk) for a total of 160 networks. Due to time constraints I
will select some reasonable fixed parameters for each random walk
(keeping the speed of the agents the same for all types of
motion). For each network I will compute the metrics presented by Tang
et al.~\cite{Tang2010} and Grindrod et al.~\cite{Grindrod2011}. To
validate the results I will generate a series of ER
graphs~\cite{Erdos1960} corresponding to each interaction network.
Each time-step in the original network will be replaced by an ER graph
with the same number of edges as the original graph in that
time-step. I will compute the same metrics for each of these
interaction networks to determine if the observed behavior can be
attributed to random chance and the number of interactions, or if it
depends on the motion of the agents.

\bibliographystyle{acm}
\bibliography{tvg-smallworld}
\end{document}