\documentclass{article}

\usepackage[letterpaper,margin=1in,top=0.5in]{geometry}

\title{Small World Behavior in Time-Varying Interaction Networks of
  Mobile Agents}

\author{Will Vining}

\begin{document}
\maketitle
\section{Introduction}
There is a great deal of research investigating the properties of
networks that are models of complex systems in nature, in particular
scale free networks~\cite{Barabasi1999} and small-world
networks~\cite{Watts1998}. Most of this work, however, is primarily
focused on static networks. Naturally occuring networks, particularly
those that describe interactions between mobile agents, are
inherrently dynamic with edges being added and removed frequently as
individual agents form new communication channels and break old
ones. These networks can be modeled as time varying
graphs~\cite{Casteigts2012,Tang2010} which describe how edges are
added and removed from the network over time. Tang et
al.~\cite{Tang2010} presented an analysis of time-varying graphs that
drew a parallel between the properties of some randomly varying graphs
and the properties of small-world graphs. The authors found that these
graphs exhibit ``small-world behavior'' when time is considered, even
if the aggregate graph (all adeges from all time steps taken together)
does not.

This work will replicate and extend the work of Tang et
al~\cite{Tang2010} who used a model of agents moving in a finite area
to generate time varying interaction networks by representing agents
as vertices and adding an edge between two agents whenever they were
close together. In this model agents move at a constant velocity and
occaisionally take large jumps to some location a large distance
away. I will extend the model by creating time-varying interaction
graphs for agents exhibiting different types of motion, in particular
correlated random walks and deterministic motion with no long random
jumps, and investigate whether the small-world behavior holds for
these graphs.

%% This represents a more physically realistic scenario than that
%% studied by Tang et al. since agents are not arbitrarily and
%% magically transported across large distances in space.

\section{Methods}
I will implement a model of agents moving on a grid and use it to
generate time varying graphs based on agent interactions (agents are
considered to interact when they are in adjacent cells). I will
implement a random walk and a deterministic walk on the grid. I will
run experiments with different numbers of agents for each type of
walker to determine if and when small-world behavior emerges.

\bibliography{tvg-smallworld}{}
\bibliographystyle{acm}

\end{document}
